TE_bilingual_vocabulary_model: Retrieve percentile information from wordbankr

### 2021-12-10 01_data_wordbank.Rmd
updated paper

# Merge the two percentile dataframe
Then we merge the two percentile dataframe by age.
```{r merge_percentile, cache = TRUE}
ws_percentile <- merge(english_ws_percentile, french_ws_percentile, 
                       by = "age") %>%
  # compute estimate total vocab by adding the two languages
  mutate(Average_10percentile = (EngWS_10percentile + FrWS_10percentile)/2,
         Average_25percentile = (EngWS_25percentile + FrWS_25percentile)/2,
         Average_50percentile = (EngWS_50percentile + FrWS_50percentile)/2,
         Average_75percentile = (EngWS_75percentile + FrWS_75percentile)/2,
         Average_90percentile = (EngWS_90percentile + FrWS_90percentile)/2) %>%
  # keep only necessary columns
  select(-c(language.x, form.x, language.y, form.y)) %>%
  # rename age to prepare for the next step (i.e., merging with keepers_ws_TE
  rename(age_months_percentile = age)

>>>>

# Merge the two percentile dataframe
Then we merge the two percentile dataframe by age.
```{r merge_percentile, cache = TRUE}
ws_percentile <- merge(english_ws_percentile, french_ws_percentile, 
                       by = "age") %>%
  # compute estimate total vocab by adding the two languages
  mutate(Average_10percentile = (EngWS_10percentile + FrWS_10percentile)/2,
         Average_25percentile = (EngWS_25percentile + FrWS_25percentile)/2,
         Average_50percentile = (EngWS_50percentile + FrWS_50percentile)/2,
         Average_75percentile = (EngWS_75percentile + FrWS_75percentile)/2,
         Average_90percentile = (EngWS_90percentile + FrWS_90percentile)/2) %>%
  # keep only necessary columns
  select(-c(language.x, form.x, language.y, form.y)) %>%
  # rename age to prepare for the next step (i.e., merging with keepers_ws_TE
  rename(age_months_percentile = age) %>%
  # round to the nearest integer
  mutate_if(is.numeric, round, digits = 0)
